Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-25 paper/paper.tex
change test -> pred (to avoid syntax highlighting of primitive test)

The Anglican language is a subset of Clojure\footnote{It would be
possible to support almost full Clojure by expanding all macros
in the Anglican source code. However, in Clojure, unlike in
Scheme~\cite{SDF+10} or Common Lisp~\cite{PC94}, the result
of macro-expansion of derived special forms is not well
specified and implementation specific.}.  Anglican queries
are defined within \texttt{defquery}. The value of the last
expression in the query body is the result of the query.
\begin{lstlisting}[style=default]
(defquery name doc-string? param? expr*)
\end{lstlisting}
Anglican functions outside of a query are defined using
\texttt{defm} with the same syntax as Clojure \texttt{defn},
however \texttt{name} is bound to an Anglican function.
\begin{lstlisting}[style=default]
(defm name doc-string? [param*] expr*)
\end{lstlisting}
Within the body of \texttt{defquery} and \texttt{defm}, the
following special forms are supported, with syntax and semantics 
matching those of Clojure:
\begin{lstlisting}[style=default]
(if test then else?)
(when test expr*)
(cond clause*)
(case expr clause* default?)
(let [binding*] expr*)
(and expr*)
(or expr*)
(fn name? [param*] expr*)
(loop [binding*] expr*)
(recur expr*)
\end{lstlisting}
In \texttt{defquery} parameter lists, \texttt{let} bindings, and
\texttt{fn} argument lists, Clojure vector destructuring is
supported. Literals for atomic types and compound literals for
vectors, hash maps, and sets are supported just like in Clojure.

>>>>

The Anglican language is a subset of Clojure\footnote{It would be
possible to support almost full Clojure by expanding all macros
in the Anglican source code. However, in Clojure, unlike in
Scheme~\cite{SDF+10} or Common Lisp~\cite{PC94}, the result
of macro-expansion of derived special forms is not well
specified and implementation specific.}.  Anglican queries
are defined within \texttt{defquery}. The value of the last
expression in the query body is the result of the query.
\begin{lstlisting}[style=default]
(defquery name doc-string? param? expr*)
\end{lstlisting}
Anglican functions outside of a query are defined using
\texttt{defm} with the same syntax as Clojure \texttt{defn},
however \texttt{name} is bound to an Anglican function.
\begin{lstlisting}[style=default]
(defm name doc-string? [param*] expr*)
\end{lstlisting}
Within the body of \texttt{defquery} and \texttt{defm}, the
following special forms are supported, with syntax and semantics 
matching those of Clojure:
\begin{lstlisting}[style=default]
(if pred then else?)
(when pred expr*)
(cond clause*)
(case expr clause* default?)
(let [binding*] expr*)
(and expr*)
(or expr*)
(fn name? [param*] expr*)
(loop [binding*] expr*)
(recur expr*)
\end{lstlisting}
In \texttt{defquery} parameter lists, \texttt{let} bindings, and
\texttt{fn} argument lists, Clojure vector destructuring is
supported. Literals for atomic types and compound literals for
vectors, hash maps, and sets are supported just like in Clojure.
